Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-03-23 revisions.qmd
Updated custom crossref YAML

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: "C. B. Smith and E. H. Hagen"
date: "`r Sys.Date()`"
output:
 bookdown::html_document2:
   number_sections: false
 bookdown::pdf_document2:
   number_sections: false
   latex_engine: xelatex
 bookdown::word_document2:
   number_sections: false
csl: apa.csl
bibliography: regrep.bib
---

>>>>

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: "C. B. Smith and E. H. Hagen"
date: "`r Sys.Date()`"
output:
 bookdown::html_document2:
   number_sections: false
 bookdown::pdf_document2:
   number_sections: false
   latex_engine: xelatex
 bookdown::word_document2:
   number_sections: false
csl: apa.csl
bibliography: regrep.bib
crossref:
  custom:
    - kind: float
      reference-prefix: Figure S
      key: sfig
      space-before-numbering: false
---
